---
title: "Concordance Precision and Accuracy"
output: word_document
---

There use to be an R package called Agreement but it has been removed from the CRAN repository.  

However, it is possible to retrieve the code for the package, which it give further below.  The code computes the concordance correlation coefficient (CCC) and measure of accuracy and precision.  Other packages can be used to compute the CCC (for example DescTools).  

For a quick overview of the CCC I would read what is posted on Wikipedia.

I believe the precision and accuracy measures produced by the code below are reasonable/valid but to be honest I am always a bit leery about code/packages that have been removed from the CRAN repository.

How I might use the code below is if the CCC is low, then I might look at the precision and accuracy to assess if the low CCC is mostly due to low accuracy or low precision.  If low accuracy you should be able determine using descrptive statistics how self-reported physical activity is systematically different from the measured physical activity.

```{r}
# library(Agreement) - removed from CRAN respository

citation(package="ICC")

#citation(package="Agreement")
```

### Agreement function from archive

```{r}
agreement <-
function(x,y,error,target,CCC_a=0.95,TDI_a,alpha=0.05,CP_a=0.9,H_label="x",V_label="y",min=NA,max=NA,by=NA,dec=2){
if (tolower(error)=="prop"){
    if ((min(y) & min(x))<=0){
        stop("For proportional error, all x and y should be greater than 0");
    }
    y <- log(y);
    x <- log(x);
}

if (tolower(error)!="prop"){
    if (is.na(min)) min <- min(min(y),min(x));
    if (is.na(max)) max <- max(max(y),max(x));
    if (is.na(by)) by <- round((max-min)/5,dec);
}else{
    if (is.na(min)) min <- exp(min(min(y),min(x)));
    if (is.na(max)) max <- exp(max(max(y),max(x)));
    if (sum(is.na(by))==1) by <- round(seq(min,max,length=7),dec);
}

d <- y-x;
m1 <- mean(y);
m2 <- mean(x);
yyy <- mean(d);
v1 <- var(y);
v2 <- var(x);
yy <- var(d);
xx <- sum(y^2);
xxx <- sum(x^2);
e2 <- sum(d^2);
n <- length(d);

if (length(y)!=length(x)) stop("x and y should have the same length!");

mu_d <- m1-m2; 
d2 <- mu_d^2;
e2 <- e2/n; 
sd2 <- (e2-d2)*n/(n-3); 
s12 <- v1*(n-1)/n; 
s22 <- v2*(n-1)/n; 
U <- mu_d/sqrt(sqrt(s12*s22)); 
V <- sqrt(s12/s22); 
Ca <- 2/(V+1/V+U**2); 
rc <- 1-e2/(d2+s12+s22); 
r <- (rc/Ca); 
d2_s2 <- (d2/sd2); 
b1 <- r*V; 
b0 <- m1-b1*m2; 
se2 <- s12*(1-r**2)*n/(n-3); 
e2 <- e2*n/(n-1);
kp <- TDI_a;
if (error=="prop"){
    kp <- log(TDI_a/100+1);
}

if (tolower(target)=="fixed"){
    di <- b0+(b1-1)*x; 
    d2i <- di^2;
    cpi <- pchisq(kp^2/se2,1,d2i/se2);
    se <- sqrt(se2); 
    kpm <- (kp+di)/se; 
    kmm <- (kp-di)/se;
    C0 <- dnorm(-kpm)-dnorm(kmm); 
    C1 <- C0*x;
    C2 <- -kpm*dnorm(-kpm)-kmm*dnorm(kmm);
    cp <- mean(cpi);
    c0 <- mean(C0);
    c1 <- mean(C1);
    c2 <- mean(C2);
    s_p <- c0^2+(c0*m2-c1)^2/s22+c2^2/2;
    if (cp<1){
        s_T <- sqrt((s_p/((n-3)*cp^2*(1-cp)^2)));
    }else{s_t <- NA;}
    if (cp<1){
        T <- log(cp/(1-cp));
    }else{T <- NA;}
    T_l <- T-qnorm(1-alpha)*s_T;
    cp_l <- exp(T_l)/(1+exp(T_l));
}

#For CCC, accuracy and precision;
L_ca <- log(Ca/(1-Ca));
z_rc <- log((1+rc)/(1-rc))/2; 
z_r <- log((1+r)/(1-r))/2; 

#For MSD & approx TDI & CP;
W <- log(e2);
k <- qnorm(1-(1-CP_a)/2)*sqrt(e2);
cp_a <- pchisq(kp^2/e2,1); 

if (tolower(target)=="fixed"){
    SZ_rc <- (1-r^2)*rc^2/((n-2)*(1-rc^2)^2*r^2)*(V*U^2*rc^2+(1-rc*r*V)^2+V^2*rc^2*(1-r^2)/2); 
    SZ_r <- (1-r^2/2)/(n-3);
    SL_ca <- (U^2*V*Ca^2*(1-r^2)+(1-V*Ca)^2*(1-r^4)/2)/((n-2)*(1-Ca)^2);
    if (s22==0){
        s_W <- 2*(1-d2^2/e2^2)/(n-2);
    }else{s_W <- 2*(1-(d2+s22*(1-b1)^2)^2/e2**2)/(n-2);}   
}else{
    SZ_rc <- ((1-r^2)*rc^2/(1-rc^2)/r^2+2*rc^3*(1-rc)*U**2/r/(1-rc^2)^2-rc^4*U^4/r^2/(1-rc^2)^2/2)/(n-2);
    SZ_r <- 1/(n-3);
    SL_ca <- ((Ca^2*U^2*(V+1/V-2*r)+Ca^2*(V^2+1/V^2+2*r^2)/2+(1+r**2)*(Ca*U^2-1))/((n-2)*(1-Ca)^2));
    s_W <- 2*(1-d2^2/e2^2)/(n-2);
}

SZ_rc <- sqrt(SZ_rc); 
SZ_r <- sqrt(SZ_r); 
SL_ca <- sqrt(SL_ca); 
s_W <- sqrt(s_W);
z_rc_l <- z_rc-qnorm(1-alpha)*SZ_rc; 
z_r_l <- z_r-qnorm(1-alpha)*SZ_r;
l_ca_l <- L_ca-qnorm(1-alpha)*SL_ca;
rc_l <- tanh(z_rc_l); 
r_l <- tanh(z_r_l); 
ca_l <- exp(l_ca_l)/(1+exp(l_ca_l));

W_u <- W+qnorm(1-alpha)*s_W;
e2_u <- exp(W_u);
k_u <- qnorm(1-(1-CP_a)/2)*sqrt(e2_u);
cp_a_l <- pchisq(kp^2/e2_u,1); 

if (tolower(error)=="prop"){
    k <- 100*(exp(k)-1); 
    k_u <- 100*(exp(k_u)-1);
}

if (tolower(target)!="fixed"){
    cp <- pchisq(kp^2/sd2,1,d2_s2); 
    sd <- sqrt(sd2); 
    kpm <- (kp+mu_d)/sd; 
    kmm <- (kp-mu_d)/sd;
    if (cp<1){ 
        s_T <- ((dnorm(-kpm)-dnorm(kmm))^2+(kmm*dnorm(kmm)+kpm*dnorm(-kpm))^2/2)/((n-3)*cp^2*(1-cp)^2); 
    }else {s_t <- NA;}  
    s_T <- sqrt(s_T);
    if (cp<1){
        T <- log(cp/(1-cp));
    }else{T <- NA;}
    T_l <- T-qnorm(1-alpha)*s_T;
    cp_l <- exp(T_l)/(1+exp(T_l));
}
conf <- (1-alpha)*100;

Data <- list(x=x,y=y,conf=conf,error=error,target=target,xlab=H_label,ylab=V_label,min=min,max=max,by=by,dec=dec)
Estimate=list(CCC=rc, Precision=r, Accuracy=Ca, TDI=k, CP=cp, RBS=d2_s2)
class(Estimate) <- "agreement"
Conf_Limit <- list(CCC=rc_l, Precision=r_l, Accuracy=ca_l, TDI=k_u, CP=cp_l, RBS=NA)
class(Conf_Limit) <- "agreement"
Allowance <- list(CCC=CCC_a, Precision=NA, Accuracy=NA, TDI=TDI_a, CP=CP_a, RBS=NA)
class(Allowance) <- "agreement"
Report <- list(Data=Data,Estimate=Estimate,Conf_Limit=Conf_Limit,Allowance=Allowance)
class(Report) <- "report"
return(Report)
}
```


# Agreement: Primary molar tooth surfaces

```{r, include=FALSE}
dmfsm <- read_sas("~/OneDrive - UW/RCDRC/PeterMilgrom/SBIR-Iodine/YearTwo/YearTwo_ExaminerCalibration/dmfs_mrgd_pm2019May16.sas7bdat")

# Next line does not do anything but run it to use same R code as further below for primary, permanent and all tooth surfaces

dmfsm1 <- dmfsm[dmfsm$primarytooth==1,]

#attributes(dmfsm1)$names
```
 
# Example code

To run the code above if you had your ordinal scores for measure_activity and sef_report_activity, the code might look like below.

```{r}
arg <- agreement(measured_activity, self_report_activity, 
                 error="const", target="random", 
                 TDI_a=sd(measured_activity))

cat("CCC")
arg$Estimate$CCC
cat("Precision")
arg$Estimate$Precision
cat("Accuracy")
arg$Estimate$Accuracy
```

The methods have been developed for continuous measures, but should be reasonable to used for ordinal data.
